Optimization of E-Commerce Product Discount Portfolio Using Modified Dynamic

### 2022-08-23 Semester II/Research Method/Paper Finale/draft.Rmd
new

---
title: "Optimization of E-Commerce Product Discount Portfolio Using Modified Dynamic Spiral Optimization Algorithm"
author: "Mohammad Rizka Fadhli"
date: |
  | Department of Computational Science, Natural Sciences Faculty, 
  | Institut Teknologi Bandung
  | Jalan Ganesha No. 10 Bandung, West Java, Indonesia
  | Corresponding author's email: 20921004@mahasiswa.itb.ac.id
affiliation: ITB
fontsize: 12pt
output: 
  pdf_document:
    number_sections: false
    toc: false
    fig_width: 7
    fig_height: 4
    fig_caption: true
    highlight: breezedark
bibliography: references.bib
csl: academic-psychiatry.csl
linestretch: 1.25
colorlinks: true
abstract: The development of the digital economy market in Indonesia is growing every year. As a result, marketplaces have to compete with each other to get consumers. Blibli.com is one of the pioneer marketplace in Indonesia has strategy to provide additional discounts on listed products. Product discount portfolio problem is a Binary Linear Programming (BLP) problem with a decision variable in the form of a binary number that states whether a product is eligible for a discount or not. With many decision variables involved, we developed metaheuristic approaches Spiral Dynamic Optimization Algorithm (SDOA) to solve the optimization problem. The SDOA solution is proven to be more optimal (generates higher revenur) than the existing Blibli.com solution by average $9.8 \%$.
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot[CO,CE]{20921004@mahasiswa.itb.ac.id}
- \fancyfoot[LE,RO]{page \thepage}
---

@@

At least we can use two methods to solve BLP: the exact method and the meta-heuristic method. Meta-heuristic methods are developing rapidly that several algorithms can quickly solve optimization problems. The meta-heuristic algorithm such as SDOA can solve BLP in a small number of decision variables involved. SDOA is an algorithm inspired by spiral motion in natural events. The rotation matrix is​an algebraic principle closely related to SDOA [@tamura]. SDOA is proven to be used to solve BLP problems by modifying the existing objective function and constraints [@kun]. The basic idea is to turn a constrained problem into an unconstrained problem by creating a penalty function.

@@

Modifikasi seperti ini memungkinkan

>>>>

---
title: Optimization of E-Commerce Product Discount Portfolio Using Modified Dynamic
  Spiral Optimization Algorithm
author: "Mohammad Rizka Fadhli"
date: "| Department of Computational Science, Natural Sciences Faculty, \n| Institut
  Teknologi Bandung\n| Jalan Ganesha No. 10 Bandung, West Java, Indonesia\n| Corresponding
  author's email: 20921004@mahasiswa.itb.ac.id\n"
output:
  pdf_document:
    number_sections: no
    toc: no
    fig_width: 7
    fig_height: 4
    fig_caption: yes
    highlight: breezedark
  word_document:
    toc: no
fontsize: 12pt
affiliation: ITB
bibliography: references.bib
csl: academic-psychiatry.csl
linestretch: 1.25
colorlinks: yes
abstract: The development of the digital economy market in Indonesia is growing every
  year. As a result, marketplaces have to compete with each other to get consumers.
  Blibli.com is one of the pioneer marketplace in Indonesia has strategy to provide
  additional discounts on listed products. Product discount portfolio problem is a
  Binary Linear Programming (BLP) problem with a decision variable in the form of
  a binary number that states whether a product is eligible for a discount or not.
  With many decision variables involved, we developed metaheuristic approaches Spiral
  Dynamic Optimization Algorithm (SDOA) to solve the optimization problem. The SDOA
  solution is proven to be more optimal (generates higher revenur) than the existing
  Blibli.com solution by average $9.8 \%$.
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot[CO,CE]{20921004@mahasiswa.itb.ac.id}
- \fancyfoot[LE,RO]{page \thepage}
---

@@

At least we can use two methods to solve BLP: the exact method and the meta-heuristic method. Meta-heuristic methods are developing rapidly that several algorithms can quickly solve optimization problems. The meta-heuristic algorithm such as SDOA can solve BLP in a small number of decision variables involved. SDOA is an algorithm inspired by spiral motion in natural events. The rotation matrix is an algebraic principle closely related to SDOA [@tamura]. SDOA is proven to be used to solve BLP problems by modifying the existing objective function and constraints [@kun]. The basic idea is to turn a constrained problem into an unconstrained problem by creating a penalty function.

@@
